Claret: Using Data Types for Highly Concurrent Distributed Transactions

### 2015-03-08 rmd/paper.Rmd
fix Dan's email (oops)

author:
  - {family: Holt,  given: Brandon, affiliation: 1, email: bholt}
  - {family: Zhang, given: Irene,   affiliation: 1, email: iyzhang}
  - {family: Ports, given: Dan,     affiliation: 1, email: dkp}
  - {family: Oskin, given: Mark,    affiliation: 1, email: oskin}
  - {family: Ceze,  given: Luis,    affiliation: 1, email: luisceze}

>>>>

author:
  - {family: Holt,  given: Brandon, affiliation: 1, email: bholt}
  - {family: Zhang, given: Irene,   affiliation: 1, email: iyzhang}
  - {family: Ports, given: Dan,     affiliation: 1, email: drkp}
  - {family: Oskin, given: Mark,    affiliation: 1, email: oskin}
  - {family: Ceze,  given: Luis,    affiliation: 1, email: luisceze}
